On the presentation of orthogonal groups over polynomial rings

### 2019-05-05 dl-paper.tex
Added root-theoretic lemma

@@

 The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
 \begin{itemize}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$
 \end{itemize}
\end{lemma}
\begin{proof}

 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi^+\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.

@@

 The next step of the proof is to write each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
  so this process is guaranteered to end.
 Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if you substitute proper values into it)
  have terms of degree at least $2$ in $X$. As a side effect of this operation, however, terms $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could have turned into
   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$.
 After collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
  we obtain the desired decomposition for $g$. \end{proof}

@@

>>>>

\begin{lemma} \label{root-lemma}
 For any $\alpha, \beta$ in a system of type $A_3$ there exist $\alpha_1, \alpha_2, \beta_1, \beta_2 \in \Phi$ such that
 $\alpha = \alpha_1 - \alpha_2$, $\beta = \beta_1 - \beta_2$ and root sets $\{ \pm \alpha, \pm \beta \}$ and $\{ \alpha_1, \alpha_2, \beta_1, \beta_2 \}$ have empty intersection.
\end{lemma}
\begin{proof} Direct calculation. \end{proof}

@@

 The group $K(A[X], M[X]) \cap P_\alpha(0) \cap P_{\beta}(0)$ admits generating set consisting of the following elements:
 \begin{itemize}
  \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
 \end{itemize}
\end{lemma}
\begin{proof}

 Embed $\alpha$ and $\beta$ in some subsystem $\Psi$ of type $A_3$ and denote by $\Sigma$ the special part of the parabolic subset $S = \Psi \cup \Phi^+$.
 Applying~\cref{thm:Stepanov} to $S$ we obtain that every element of $\St(\Phi, A[X], XM[X])$ can be presented as a product of 
  $z_\gamma(Xf, \xi)$, $\gamma \in \Sigma(S) \subseteq \Phi\setminus \{ \pm \alpha, \pm \beta \}$ and $x_\gamma(Xf)$, $\gamma \in \{ \pm \alpha, \pm \beta \}$.

@@

 The next step of the proof is to decompose each factor of the form $x_{\epsilon}(Xf)$, $\epsilon \in \{-\alpha,-\beta\}$ appearing in this product as
 $x_{\epsilon}(X^2f') \cdot x_{\epsilon}(mX)$ and then move $x_{\epsilon}(mX)$ to the rightmost position
  (conjugating by $x_{\epsilon}(mX)$ all factors along the way).
 Notice that no terms of the form $x_{\epsilon}(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ may appear after the simplification of conjugates,
  so this process is guaranteed to terminate.
 Indeed, notice that the extra terms in the right-hand sides of \eqref{eq3-1} and~\eqref{eq3-2} 
 (as well as all terms in the right-hand sides of~\eqref{C1},\eqref{C2} of~\cref{Crels} if one substitutes corresponding values into it)
  have terms of degree at least $2$ in $X$.

 As a side effect of this transformation, however, factors $x_\alpha(Xf)$ and $x_\beta(Xf)$ appearing in $g$ could be transformed into terms of the form
   $z_\alpha(Xf, X\xi)$, and $z_\beta(Xf, X\xi)$. Applying preceding lemma to the subsystem $\Psi$ we can write $\alpha = \alpha_1 - \alpha_2$ and 
    $\beta = \beta_1 - \beta_2$ with the additional property $\{ \pm \alpha, \pm \beta \} \cap \{ \alpha_1, \alpha_2, \beta_1, \beta_2 \} = \emptyset$.
 Invoking~\eqref{Z5} of~\cref{Zrels} with $\alpha = \alpha_1$, $\beta = -\alpha_2$, $\eta = 1$, $s = Xf$, $\xi = X\xi$ we can rewrite the term
  $z_\alpha(Xf, X\xi)$ as a product of terms from the statement of the lemma. Similar argument also applies to $z_\beta(Xf, X\xi)$.

 Finally, after collecting terms of the form $x_\epsilon(mX)$, $\epsilon \in \{ -\alpha, -\beta \}$ in the right-hand side of the resulting expression
  we obtain the desired decomposition for $g$. \end{proof}

@@

\begin{lemma}
 Let $\alpha, \beta \in \Phi$ be such that $\langle \alpha,\beta \rangle = 0$ or $1$.
 Then the image of $K(A[X], M[X]) \cap P_\alpha(0) \cap P_\beta(0)$ under $S_{\alpha}(a, -)$ is contained in the subgroup of $\St(\Phi, A[X, X^{-1}])$
  generated by the following elements:
  \begin{enumerate}
   \item $z_\gamma(Xf, \xi)$, $\gamma \in \Phi \setminus\{ \pm \alpha, \pm \beta\};$
   \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$, $z_{\alpha}(Xf, X\xi)$, $z_\beta(Xf, X\xi)$;
   \item $c_{\pm \delta}(f, X\xi)$ for some fixed root $\delta \in \Phi$, $\delta \not \in \{ \pm \alpha, \pm \beta \}$.
  \end{enumerate}
 In particular, this image is contained in $P_\beta(0)$.
\end{lemma}
\begin{proof}
Lol
\end{proof}
